HTLSDstack

### 2025-06-16 Code/R/Research/HTLSDstack.Rmd
2 semester report first draft

# Example 1
plot_name <- "complex_param_rmse"
A <- c(1, 1)
phi <- c(0, 0)
rate <- c(0, 0)
freq <- c(0.2, 0.205)
L_esprit <- 500
L_htlsd <- 50
L_tens <- 50
D <- 10
groups_esprit <- list(1:2)
groups_htlsd <- list(1:2)
groups_tens <- list(1:2)
r3_1 <- 2
r3_2 <- 1
est_dim <- 1
dt <- 0.1
N <- 999

@@

# Real case with same parameters by L
```{r}
plot_name <- "real_param_rmse"
N <- 999
A <- c(1, 1)
phi <- c(0, 0)
rate <- c(0, 0)
freq <- c(0.2, 0.205)
D <- 10
Ls_esprit <- as.integer(seq(from = N %/% 3, to = 2 * N %/% 3, length.out = 20))
Ls_dstack <- as.integer(seq(from = (N %/% D) %/% 3, to = 2 * (N %/% D) %/% 3, length.out = 20))
groups_esprit <- list(1:4)
groups_htlsd <- list(1:4)
groups_tens <- list(1:4)
r3_1 <- 4
r3_2 <- 1
est_dim <- 1
dt <- 0.1

@@

  p2 <- rmse_df |> filter(sd == sd_k) |>
    pivot_longer(cols = esprit:tens2,
                 names_to = "Method",
                 values_to = "RMSE") |>
    filter(Method != "esprit") |>
    ggplot(aes(x = Ls_htlsd, y = RMSE)) +
    geom_line(aes(col = Method, lty = Method)) +
    geom_hline(
      yintercept = min(ext_rmse_esprit$min),
      linetype = 2,
      color = "gray20"
    ) +
    annotate(
      "label",
      x = (Ls_htlsd[Ls_len] + Ls_htlsd[1]) * 0.38,
      y = min(ext_rmse_esprit$min) * 1.015,
      label = paste0("Minimum for ESPRIT")
    ) +
    scale_linetype_discrete(labels = c("HTLSDstack", "Tensor, r3 = 4", "Tesnor, r3 = 1")) +
    scale_color_discrete(labels = c("HTLSDstack", "Tensor, r3 = 4", "Tesnor, r3 = 1")) +
    ggtitle(paste0("Dstack methods, sd = ", sd_k)) +
    theme_minimal() +
    xlab("L")
  pdf(paste0("./img/htlsd_byL_", plot_name, "_esprit_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p1)
  dev.off()
  pdf(paste0("./img/htlsd_byL_", plot_name, "_dstack_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p2)
  dev.off()
  print(p1)
  print(p2)
}
```

@@

  p2 <- rmse_df |> filter(sd == sd_k) |>
    pivot_longer(cols = ssa:tens1,
                 names_to = "Method",
                 values_to = "RMSE") |>
    filter(Method != "ssa") |>
    ggplot(aes(x = Ls_dstack, y = RMSE)) +
    geom_line(aes(col = Method, lty = Method)) +
    geom_hline(
      yintercept = min(ext_rmse_esprit$min),
      linetype = 2,
      color = "gray20"
    ) +
    annotate(
      "label",
      x = (Ls_dstack[Ls_len] + Ls_dstack[1]) * 0.38,
      y = min(ext_rmse_esprit$min) * 1.01,
      label = paste0("Minimum for SSA")
    ) +
    scale_linetype_discrete(labels = c("SSADstack", "Tensor, r3 = 4")) +
    scale_color_discrete(labels = c("SSADstack", "Tensor, r3 = 4")) +
    ggtitle(paste0("Dstack methods, sd = ", sd_k)) +
    theme_minimal() +
    xlab("L")
  pdf(paste0("./img/htlsd_byL_", plot_name, "_ssa_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p1)
  dev.off()
  pdf(paste0("./img/htlsd_byL_", plot_name, "_dstack_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p2)
  dev.off()
  print(p1)
  print(p2)
}
```

>>>>

# Example 1
plot_name <- "complex_param_rmse"
A <- c(1, 1)
phi <- c(0, 0)
rate <- c(0, 0)
freq <- c(0.2, 0.205)
L_esprit <- 500
L_htlsd <- 50
L_tens <- 50
D <- 10
groups_esprit <- list(1:2)
groups_htlsd <- list(1:2)
groups_tens <- list(1:2)
r3_1 <- 2
r3_2 <- 1
est_dim <- 1
dt <- 0.1
N <- 990

@@

# Real case with same parameters by L
```{r}
plot_name <- "real_param_rmse"
N <- 990
A <- c(1, 1)
phi <- c(0, 0)
rate <- c(0, 0)
freq <- c(0.2, 0.205)
D <- 10
Ls_esprit <- as.integer(seq(from = N %/% 3, to = 2 * N %/% 3, length.out = 20))
Ls_dstack <- as.integer(seq(from = (N %/% D) %/% 3, to = 2 * (N %/% D) %/% 3, length.out = 20))
groups_esprit <- list(1:4)
groups_htlsd <- list(1:4)
groups_tens <- list(1:4)
r3_1 <- 4
r3_2 <- 1
est_dim <- 1
dt <- 0.1

@@

  p2 <- rmse_df |> filter(sd == sd_k) |>
    pivot_longer(cols = esprit:tens2,
                 names_to = "Method",
                 values_to = "RMSE") |>
    filter(Method != "esprit") |>
    ggplot(aes(x = Ls_htlsd, y = RMSE)) +
    geom_line(aes(col = Method, lty = Method)) +
    geom_hline(
      yintercept = min(ext_rmse_esprit$min),
      linetype = 2,
      color = "gray20"
    ) +
    annotate(
      "label",
      x = (Ls_dstack[Ls_len] + Ls_dstack[1]) * 0.38,
      y = min(ext_rmse_esprit$min) * 1.015,
      label = paste0("Minimum for ESPRIT")
    ) +
    scale_linetype_discrete(labels = c("Dstack ESPRIT", "Tensor, r3 = 4", "Tesnor, r3 = 1")) +
    scale_color_discrete(labels = c("Dstack ESPRIT", "Tensor, r3 = 4", "Tesnor, r3 = 1")) +
    ggtitle(paste0("Dstack methods, sd = ", sd_k)) +
    theme_minimal() +
    xlab("L")
  pdf(paste0("./img/htlsd_byL_", plot_name, "_esprit_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p1)
  dev.off()
  pdf(paste0("./img/htlsd_byL_", plot_name, "_dstack_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p2)
  dev.off()
  print(p1)
  print(p2)
}
```

@@

  p2 <- rmse_df |> filter(sd == sd_k) |>
    pivot_longer(cols = ssa:tens1,
                 names_to = "Method",
                 values_to = "RMSE") |>
    filter(Method != "ssa") |>
    ggplot(aes(x = Ls_dstack, y = RMSE)) +
    geom_line(aes(col = Method, lty = Method)) +
    geom_hline(
      yintercept = min(ext_rmse_esprit$min),
      linetype = 2,
      color = "gray20"
    ) +
    annotate(
      "label",
      x = (Ls_dstack[Ls_len] + Ls_dstack[1]) * 0.38,
      y = min(ext_rmse_esprit$min) * 1.01,
      label = paste0("Minimum for SSA")
    ) +
    scale_linetype_discrete(labels = c("Dstack SSA", "Tensor, r3 = 4")) +
    scale_color_discrete(labels = c("Dstack SSA", "Tensor, r3 = 4")) +
    ggtitle(paste0("Dstack methods, sd = ", sd_k)) +
    theme_minimal() +
    xlab("L")
  pdf(paste0("./img/htlsd_byL_", plot_name, "_ssa_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p1)
  dev.off()
  pdf(paste0("./img/htlsd_byL_", plot_name, "_dstack_", which(sds == sd_k), ".pdf"),
      width = 9,
      height = 7)
    print(p2)
  dev.off()
  print(p1)
  print(p2)
}
```
